\bf Faster Neural Machine Translation Inference

### 2018-02-08 fast-beam/fast-beam.tex
fast beam paper

Our paper follows most closely on from ~\cite{DBLP:conf/emnlp/Devlin17} which achieved faster NMT inference mainly by novel implementation of an existing model. However, we differ by focusing on GPU implementation, and the output layer and batching algorithm which were not touched on by the previous work.

@@

In fact, we are usually only interested in the best class during inference, not the probability. Therefore, we can skip the second iteration over $p$ in Algorithm~\ref{algo:Fused Kernel} and avoid computing the softmax altogether, Algorithm~\ref{algo:Argmax only}.

@@

It has been noted by ~\citep{koehn-knowles:2017:NMT} and others that using n-best number of classes, rather than just the best class, improves translation quality. Unlike the 1-best case, however, the softmax calculation cannot be skipped as the denominator differs for each input.

>>>>

Our paper follows most closely on from ~\cite{DBLP:conf/emnlp/Devlin17} which achieved faster NMT inference mainly by novel implementation of an existing model. However, we differ by focusing on GPU implementation, specifically the output layer, and the batching algorithm which were not touched on by the previous work.

@@

In fact, we are usually only interested in the best class during inference, not the probability. Since we now calculate the best class before the softmax, we can skip softmax altogether, Algorithm~\ref{algo:Argmax only}. However, is this only possible for beam size 1; the comparison between softmax probobilities is required for larger beam sizes as the denominator is different in different beams.

@@
